Maintenance planning on French military aircraft operations

### 2018-08-30 R/presentations/CLAIO_presentation/presentation.Rmd

if (show_gantt){
    # htmltools::HTML('<div style="font-size: 20px;width:100%">')
    # htmltools::div(style="font-size: 20px;width:100%", gantt)
    gantt
    # htmltools::HTML("</div>")
} else {
    knitr::include_graphics('../img/calendar.png' %>% paste0(path_to_R_dir, .))
}

@@

if (show_gantt){
    htmltools::div(class = "row",
        htmltools::div(task_gantt, class = "col-md-6")
        ,htmltools::div(task_employees, class = "col-md-6")
        )
} else {
    knitr::include_graphics(c('../img/tasks-days.png', '../img/task-employees.png') %>% paste0(path_to_R_dir, .))
    # knitr::include_graphics('../img/task-employees.png' %>% paste0(path_to_R_dir, .))
}

>>>>

if (show_gantt){
    gantt
} else {
    knitr::include_graphics('../img/calendar.png' %>% paste0(path_to_R_dir, .))
}

@@

if (show_gantt){
    htmltools::div(class = "row",
        htmltools::div(task_gantt, class = "col-md-6")
        ,htmltools::div(task_employees, class = "col-md-6")
        )
} else {
    c('../img/tasks-days.png', '../img/task-employees.png') %>% paste0(path_to_R_dir, .) %>% 
    knitr::include_graphics
    # knitr::include_graphics('../img/task-employees.png' %>% paste0(path_to_R_dir, .))
}
